Data Preparation, Integration and Cleaning

### 2018-05-09 scripts/3_data_prep.Rmd
Reorder and clean up past Location

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(geosphere)
  library(ggmap)
  library(xtable)
  library(sp)
  library(rgeos)
  library(reshape2)
  library(stringr)
  library(RColorBrewer)
  # library(Hmisc)
  library(multidplyr)
  library(lubridate)
  library(tidyverse)
  library(sf)

@@

  source(file.path(code_path, 'functions', 'abb_Functions.R'))

#
#  # Other custom files
# 
#   if(offline){
# 
#     source(file.path(code_path, 'tools', 'dataVizTools', 'ggPlotTools.R'))
#     source(file.path(code_path, 'tools', 'datamgmttools', 'dataMungeTools.R'))
#     source(file.path(code_path, 'tools', 'spatialTools', 'spatialLogitModels.R'))
#     source(file.path(code_path, 'tools', 'spatialTools', 'point2surface_Tools.R'))
#     
#   } else {
#     
#   source(paste0('https://raw.githubusercontent.com/andykrause/dataVizTools',
#                 '/master/ggPlotTools.R'))
#   source(paste0('https://raw.githubusercontent.com/andykrause/datamgmttools',
#                 '/master/dataMungeTools.R'))
#   source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
#                 '/master/spatialLogitModels.R'))
#   source(paste0('https://raw.githubusercontent.com/andykrause/spatialTools',
#                 '/master/point2surface_Tools.R'))
# 
#   }
```

@@

 # Set all colors

  abb_colors.names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 'beach',
                     'ebisu', 'tirol', 'foggy', 'hof')
  abb_col <- c(rgb(250,88,99, maxColorValue=255), rgb(139,14,82, maxColorValue=255),
               rgb(0,117,140, maxColorValue=255), rgb(4,211,191, maxColorValue=255),
               rgb(77,226,110, maxColorValue=255), rgb(252,179,14, maxColorValue=255),
               rgb(249,177,139, maxColorValue=255), rgb(191,166,100, maxColorValue=255),
               rgb(156,161,155, maxColorValue=255), rgb(86,94,97, maxColorValue=255))

 # Set specific colors

  str_col <- abb_col[1]
  ltr_col <- abb_col[3]

@@

```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

And, finally, we load three GIS shapefiles.  The first two denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area. We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.]  After we load each we convert the names of the data fields to lower case for easier use in future coding.

```{r load_sp_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

```{r initialCC, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

```{r add_month, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

```{r fix_type, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

```{r plot_type_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}

   # Create Airbnb plot

   str_types <- ggplot(str_tdf, aes(x=type)) + 
     geom_bar(color=str_col, fill=str_col) +
     xlab('\nProperty Type\n') + 
     ggtitle('\nShort Term Rentals\n')  +
     ylab('# of Properties\n') +
     theme(plot.title = element_text(hjust = 0.5))

@@

  ltr_types <- ggplot(ltr_tdf, aes(x=type)) +
    geom_bar(color=ltr_col, fill=ltr_col) +
    xlab('\nProperty Type\n') +
    ggtitle('\nLong Term Rentals\n')  +
    ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

  str_types
  ltr_types

  # Output plots
  # png(file=paste0(fig.path, 'dataclean_proptype.png'), width = 480, height = 280,
  #     bg='transparent')
  #  ggMultiPlots(str_types, ltr_types, cols=2)
  # dev.off()
# 
#   save(str.types, file=paste0(fig.path, 'strtypes.RData'))
#   save(ltr.types, file=paste0(fig.path, 'ltrtypes.RData'))

@@

```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}

@@

   # Count Cleaning
   countCleaning('property.type')

@@

```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE, fig.height=4}

@@

   list_types <- ggplot(str_tdf, aes(x=listing_type)) + 
      geom_bar(color=str_col, fill=str_col) +
      xlab('\nListing Type\n') +
      ggtitle('\nShort Term Rentals by Listing Type\n')  +
      ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

  # # Make Plot
  # png(file=paste0(fig.path, 'dataclean_listtype.png'), width = 480, height = 280,
  #     bg='transparent')
  # 
  #   list.types
  # 
  # dev.off()
  # 
  # save(list.types, file=paste0(fig.path, 'listtypes.RData'))

@@

```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

```{r bed_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

  # Build long term bar plot

    ltrbed <- ggplot(ltr_tdf, aes(x=bedrooms)) + 
     geom_bar(fill=ltr_col, color=ltr_col) +
     facet_wrap(~type,scales='free_y') +
     scale_x_continuous(labels=1:10, breaks=1:10)+
     xlab('\nBedrooms\n') +
     scale_y_continuous(labels=c(0,10000,20000), 
                        breaks=c(0,10000,20000))+
     ylab('') +
     ggtitle('Bedrooms in Long Term Rentals') +
     theme(plot.title = element_text(hjust = 0.5))

  # Build short term bar plot

   strbed <- ggplot(str_tdf, aes(x=bedrooms)) + 
     geom_bar(fill=str_col, color=str_col) +
     facet_wrap(~type,scales='free_y') +
     scale_x_continuous(labels=0:10, breaks=0:10) +
     xlab('\nBedrooms\n') +
     ylab('') +
     ggtitle('Bedrooms in Short Term Rentals') +
     theme(plot.title = element_text(hjust = 0.5))

#   # Make Plot
#   png(file=paste0(fig.path, 'dataclean_bedcount.png'), width = 480, height = 280, 
#       bg='transparent')
#     ggMultiPlots(strbed, ltrbed, cols=1)
#   dev.off()
#   
#   save(ltrbed, file=paste0(fig.path, 'ltrbed.RData'))
#   save(strbed, file=paste0(fig.path, 'strbed.RData'))

@@

```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Remove all with more than 4 beds for house, 3 beds for apt and convert studio to 1 bed

   str_df <- str_tdf %>% 
     dplyr::filter(bedrooms < 5) %>%
     dplyr::filter(type == 'House' | (type == 'Apartment' & bedrooms < 4)) %>%
     dplyr::mutate(bedrooms == if_else(bedrooms == 0, 1L, bedrooms))

   ltr_df <- ltr_tdf %>% 
     dplyr::filter(bedrooms < 5) %>%
     dplyr::filter(type == 'House' | (type == 'Apartment' & bedrooms < 4)) %>%
     dplyr::mutate(bedrooms == if_else(bedrooms == 0, 1, bedrooms))

@@

```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Remove missing data
  ltr_tdf <- ltr_tdf %>%
    dplyr::rename(bathrooms = baths) %>%
    dplyr::filter(!is.na(bathrooms))
  str_tdf <- str_tdf %>% dplyr::filter(!is.na(bathrooms))

@@

```{r bath_fltr2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

  # Build long term plot

   ltbath <- ggplot(ltr_tdf, aes(x=bathrooms)) + 
     geom_bar(fill=ltr_col, color=ltr_col) +
     facet_wrap(~type) +
     scale_x_continuous(labels=1:8, breaks=1:8)+
     xlab('\nBathrooms\n') +
     ylab('') +
     ggtitle('Bathrooms in Long Term Rentals') +
     theme(plot.title = element_text(hjust = 0.5))

 # Build short term plot

  stbath <- ggplot(str_tdf, aes(x=bathrooms)) +
    geom_bar(fill=str_col, color=str_col) +
    facet_wrap(~type, scales='free_y') +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('\nBathrooms\n') +
    ylab('') +
    ggtitle('Bathrooms in Short Term ltrals') +
    theme(plot.title = element_text(hjust = 0.5))

#  # Make Plots  
#   png(file=paste0(fig.path, 'dataclean_bathount.png'), width = 480, height = 280, 
#       bg='transparent')
#   
#     ggMultiPlots(stbath, ltbath, cols=1)
#     
#   dev.off()
#    
#   save(ltbath, file=paste0(fig.path, 'ltrbath.RData'))
#   save(stbath, file=paste0(fig.path, 'strbath.RData'))

@@

```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 # Create combination variable
  str_tdf <- str_tdf %>% 
    dplyr::mutate(bedbath = paste0(bedrooms, "_", bathrooms))

@@

```{r filtBB2, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

 # Make long term plot

  ltbb <- ggplot(ltr_tdf, aes(x=bedbath)) +
    geom_bar(fill=ltr_col, color=ltr_col) +
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ggtitle('Long Term Rentals') +
    facet_wrap(~type, scales='free_y')+
    theme(plot.title = element_text(hjust = 0.5))

 # Make short term plots

  stbb <- ggplot(str_tdf, aes(x=bedbath)) +
    geom_bar(fill=str_col, color=str_col) +
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    ggtitle('Short Term Rentals') +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    facet_wrap(~type, scales='free_y')+
    theme(plot.title = element_text(hjust = 0.5))

#  # Make Plots  
#   png(file=paste0(fig.path, 'dataclean_bedbath.png'), width = 480, height = 280, 
#       bg='transparent')

#     ggMultiPlots(ltbb, stbb, cols=1)

#   dev.off()

#   save(ltbb, file=paste0(fig.path, 'ltrbb.RData'))
#   save(stbb, file=paste0(fig.path, 'strbb.RData'))

@@

From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2 and 4/2. We filter the data to these combinations.  We also combine type and bed bath combination to create a 'product'.

```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

  acc_bb <- c('1_1', '2_1', '2_2', '3_1', '3_2', '4_2')

@@

@@

```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

```{r mappoints, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Convert shapefile to ggplot-able object

   # Limit to extent of data
   ltr_subs <- ltr_tdf %>%
    dplyr::select(suburb) %>%
    group_by(suburb) %>%
    summarize(count=n())

   # Clip to only those with a ltral observation
   studysubs_sf <- sub_sf %>%
     filter(NAME_2006 %in% ltr_subs$suburb)

   # Convert to an outer bound with holes
   ss_bound <- st_union(studysubs_sf)

   # ss.bound <- gUnaryUnion(study.suburbs)
   # 
   # # Remove holes from the shapefile
   # ssb <- slot(ss.bound, "polygons") 
   # holes <- lapply(ssb, function(x) sapply(slot(x, "Polygons"), 
   #                                         slot, "hole"))
   # res <- lapply(1:length(ssb), function(i) slot(ssb[[i]], "Polygons")[!holes[[i]]]) 
   # IDs <- row.names(ss.bound) 
   # ssb.fill <- SpatialPolygons(lapply(1:length(res), function(i) 
   #  Polygons(res[[i]], ID=IDs[i])), proj4string=CRS(proj4string(ss.bound))) 
   # 
   # # Identify which suburbs all in area covered by outer bound
   # ss.in <- gIntersects(suburbs.shp, ssb.fill, byid=T)
   # study.suburbs <- suburbs.shp[which(ss.in), ]
   # 
   # # Convert into an outer boundary with no holes
   # ss.bound.out <- gUnaryUnion(study.suburbs)
   # ssb.out <- slot(ss.bound.out, "polygons") 
   # holes <- lapply(ssb.out, function(x) sapply(slot(x, "Polygons"), 
   #                                         slot, "hole"))
   # res.out <- lapply(1:length(ssb.out), 
   #                   function(i) slot(ssb.out[[i]], "Polygons")[!holes[[i]]]) 
   # IDs <- row.names(ss.bound.out) 
   # ssb.fill.out <- SpatialPolygons(lapply(1:length(res.out), 
   #                                        function(i) Polygons(res.out[[i]], 
   #                                                             ID=IDs[i])),
   #                                             proj4string=CRS(proj4string(ss.bound))) 
   # 
   # # Convert into a ggplot-able format
   # subs <- fortify(study.suburbs, region='name_2006')
   # 
   # # Add suburb category
   # subs$des <- suburbs.shp@data$suburbdesi[
   #   match(subs$id, suburbs.shp@data$name_2006)]

#    # Set colors
#    g_cols <- c('grey10', 'grey40', 'grey70')
#  
#    # Make map
#    ggplot(studysubs_sf) %>%
#      geom_sf(aes(group=group, fill=suburbDesi))
# 
#    loc_map <- ggplot() +
#      geom_polygon(data=studysubs_sf, 
#                   aes(x=long, y=lat, group=group, fill=des), alpha=.8) + 
# #     scale_fill_manual(values=g_cols, labels=c('Inner      ',
#                                               'Middle      ',
#                                               'Outer')) +
#     geom_path(data=subs[subs$des=='Outer', ], 
#               aes(x=long, y=lat, group=group), col='white', size=.1,
#               linetype=1) +
#   
#     geom_path(data=subs[subs$des=='Middle', ], 
#               aes(x=long, y=lat, group=group), col='grey70', size=.1,
#               linetype=1) +
#     
#     geom_path(data=subs[subs$des=='Inner', ], 
#               aes(x=long, y=lat, group=group), col='grey40', size=.1,
#               linetype=1) +
#     
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     #ggtitle("Melbourne Suburb Classifications")+
#     theme(plot.title = element_text(hjust = 0.5))
# 
# ```
# 
# ```{r plot_loc_map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=6}
#   png(file=paste0(fig.path, 'locationmap.png'), width = 480, height = 390, 
#       bg='transparent')
#   
#     loc.map
#     
#   dev.off()
#   
#   loc.map
#   
#   save(loc.map, file=paste0(fig.path, 'suburbMap.RData'))
# 
#     
```
# 
It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.  While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.  Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:

```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  beach_buffer <- st_buffer(beach_sf, dist =(500 / m_conv))

```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ## Short term data

 # Convert to point shapefile
   str_tdf <- st_as_sf(str_tdf,
                       coords = c('longitude', 'latitude'),
                       crs = 4283)

   ltr_tdf <- st_as_sf(ltr_tdf %>% dplyr::filter(!is.na(latitude)),
                       coords = c('longitude', 'latitude'),
                       crs = 4283)

    str_tdf <- st_join(str_tdf, 
                       sub_sf %>% 
                        dplyr::select(suburb = NAME_2006,
                                      sub_des = suburbDesi,
                                      geometry)) %>%
    dplyr::filter(!is.na(sub_des))

    ltr_tdf <- st_join(ltr_tdf %>%
                         dplyr::select(-suburb), 
                       sub_sf %>% 
                        dplyr::select(suburb = NAME_2006,
                                      sub_des = suburbDesi,
                                      geometry)) %>%
    dplyr::filter(!is.na(sub_des))

    sub_str <- str_tdf %>% 
      dplyr::select(suburb, -geometry) %>% 
      as.tibble() %>%
      dplyr::group_by(suburb) %>% 
      dplyr::summarize(count=n())

    sub_ltr <- ltr_tdf %>% 
      dplyr::select(suburb, -geometry) %>% 
      as.tibble() %>%
      dplyr::group_by(suburb) %>% 
      dplyr::summarize(count=n())

    str_tdf <- str_tdf %>%
      dplyr::filter(suburb %in% sub_all$suburb)

    ltr_tdf <- ltr_tdf %>%
      dplyr::filter(suburb %in% sub_all$suburb)

    str_tdf <- st_join(str_tdf, 
                       sa1_sf %>%
                         dplyr::select(sa1=SA1_MAIN11,
                                       geometry)) %>%
    dplyr::filter(!is.na(sa1))

>>>>

  library(tidyverse)
  library(sf)
  library(geosphere)
  library(ggmap)
  library(multidplyr)
  # library(lubridate)
  # library(spdep)
  # library(maptools)
  # library(ggplot2)

@@

  source(file.path(code_path, 'functions', 'abb_Functions.R'))
  source(file.path(code_path, 'functions', 'geom_sf.R'))

@@

 # Set all colors
  col_df <- data.frame(names=c('rausch', 'hackberry', 'kazan', 'babu', 'lima', 
                               'beach', 'ebisu', 'tirol', 'foggy', 'hof'),
                       rgb = c(rgb(250,88,99, maxColorValue=255), 
                               rgb(139,14,82, maxColorValue=255),
                               rgb(0,117,140, maxColorValue=255), 
                               rgb(4,211,191, maxColorValue=255),
                               rgb(77,226,110, maxColorValue=255), 
                               rgb(252,179,14, maxColorValue=255),
                               rgb(249,177,139, maxColorValue=255), 
                               rgb(191,166,100, maxColorValue=255),
                               rgb(156,161,155, maxColorValue=255), 
                               rgb(86,94,97, maxColorValue=255)))

 # Set specific colors
  str_col <- col_df$rgb[1]
  ltr_col <- col_df$rgb[3]
  sm_col <- col_df$rgb[c(2,4,5,8,6)]

@@

```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@

And, finally, we load three GIS shapefiles.  The first two denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area. We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.]

```{r load_sp_data, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@

```{r initialCC, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@

```{r add_month, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@

```{r fix_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@

```{r plot_str_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=4}

   ggplot(str_tdf, aes(x=type)) + 
     geom_bar(color=str_col, fill=str_col) +
     xlab('\nProperty Type\n') + 
     ggtitle('\nShort Term Rentals\n')  +
     ylab('# of Properties\n') +
     theme(plot.title = element_text(hjust = 0.5))

```{r plot_ltr_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=4}

@@

  ggplot(ltr_tdf, aes(x=type)) +
    geom_bar(color=ltr_col, fill=ltr_col) +
    xlab('\nProperty Type\n') +
    ggtitle('\nLong Term Rentals\n')  +
    ylab('# of Properties\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

```{r remove_others, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=4}

@@

   # Count Cleaning
   countCleaning('property_type')

@@

```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=4}

@@

   ggplot(str_tdf, aes(x=listing_type)) + 
      geom_bar(color=str_col, fill=str_col) +
      xlab('\nListing Type\n') +
      ggtitle('\nShort Term Rentals by Listing Type\n')  +
      ylab('# of Properties\n') +
     theme(plot.title = element_text(hjust = 0.5))

@@

```{r keep_entire_home, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@

```{r bed_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@

```{r plot_ltr_bed, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

   ggplot(ltr_tdf, aes(x=bedrooms)) + 
     geom_bar(fill=ltr_col, color=ltr_col) +
     facet_wrap(~type,scales='free_y') +
     scale_x_continuous(labels=1:10, breaks=1:10)+
     xlab('\nBedrooms\n') +
     scale_y_continuous(labels=c(0,10000,20000), 
                        breaks=c(0,10000,20000))+
     ylab('') +
     ggtitle('Bedrooms in Long Term Rentals') +
     theme(plot.title = element_text(hjust = 0.5))

```{r plot_str_bed, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

   ggplot(str_tdf, aes(x=bedrooms)) + 
     geom_bar(fill=str_col, color=str_col) +
     facet_wrap(~type,scales='free_y') +
     scale_x_continuous(labels=0:10, breaks=0:10) +
     xlab('\nBedrooms\n') +
     ylab('') +
     ggtitle('Bedrooms in Short Term Rentals') +
     theme(plot.title = element_text(hjust = 0.5))

@@

```{r bed_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  # Remove all with more than 4 beds for house, 3 beds for apt 
  str_tdf <- str_tdf %>% 
    dplyr::filter(bedrooms < 5) %>%
    dplyr::filter(type == 'House' | (type == 'Apartment' & bedrooms < 4)) 
  ltr_df <- ltr_tdf %>% 
    dplyr::filter(bedrooms < 5) %>%
    dplyr::filter(type == 'House' | (type == 'Apartment' & bedrooms < 4))

  # Convert any studio to 1 bedrooms
  str_tdf$bedrooms <- ifelse(str_tdf$bedrooms == 0, 1L, str_tdf$bedrooms)
  ltr_tdf$bedrooms  <- ifelse(ltr_tdf$bedrooms == 0, 1, ltr_tdf$bedrooms)

@@

```{r bath_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  if ('baths' %in% names(ltr_tdf)) ltr_tdf <- ltr_tdf %>% rename(bathrooms = baths)

  ltr_tdf <- ltr_tdf %>%
    dplyr::filter(!is.na(bathrooms))

  str_tdf <- str_tdf %>% 
    dplyr::filter(!is.na(bathrooms))

@@

```{r plot_ltr_bath, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

   ggplot(ltr_tdf, aes(x=bathrooms)) + 
     geom_bar(fill=ltr_col, color=ltr_col) +
     facet_wrap(~type) +
     scale_x_continuous(labels=1:8, breaks=1:8)+
     xlab('\nBathrooms\n') +
     ylab('') +
     ggtitle('Bathrooms in Long Term Rentals') +
     theme(plot.title = element_text(hjust = 0.5))

```{r plot_str_bath, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

  ggplot(str_tdf, aes(x=bathrooms)) +
    geom_bar(fill=str_col, color=str_col) +
    facet_wrap(~type, scales='free_y') +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('\nBathrooms\n') +
    ylab('') +
    ggtitle('Bathrooms in Short Term ltrals') +
    theme(plot.title = element_text(hjust = 0.5))

@@

```{r bath_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@

```{r filtBB, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  str_tdf <- str_tdf %>% 
    dplyr::mutate(bedbath = paste0(bedrooms, "_", bathrooms))

@@

```{r plot_ltr_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

  ggplot(ltr_tdf, aes(x=bedbath)) +
    geom_bar(fill=ltr_col, color=ltr_col) +
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ggtitle('Long Term Rentals') +
    facet_wrap(~type, scales='free_y')+
    theme(plot.title = element_text(hjust = 0.5))

@@

```{r plot_str_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.height=5}

  ggplot(str_tdf, aes(x=bedbath)) +
    geom_bar(fill=str_col, color=str_col) +
    xlab('\nBed/Bath Combo\n') +
    ylab('Number of Properties\n') +
    ggtitle('Short Term Rentals') +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    facet_wrap(~type, scales='free_y')+
    theme(plot.title = element_text(hjust = 0.5))

From this analysis we see that there are 6 combinations that make up most all properties:  1bed/1bath, 2/1, 2/2, 3/1, 3/2, 3/3, 4/2 and 4/3. We filter the data to these combinations.  We also combine type and bed bath combination to create a 'product'.

```{r filtBB3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@

  acc_bb <- c('1_1', '2_1', '2_2', '3_1', '3_2', '3_3', '4_2', '4_3')

@@

#### Host Policies

Here we combine the two Strict (regular and super) cancellation policies into one as there are few 'super' strict and this is used as a factor in future modeling.  We also remove the few observations with missing host policy data

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  str_tdf <- str_tdf %>%
    dplyr::mutate(canc_policy = ifelse(canc_policy == 'Super Strict 60 Days',
                                         'Strict', canc_policy)) %>%
    dplyr::filter(canc_policy %in% c('Flexible', 'Moderate', 'Strict'))

  # Count Cleaning
  countCleaning('hostpolicy')

### Location

  # Set colors
  tm_shape(sub_sf) +
    tm_polygons('suburbDesi',
                title='Suburb Designation',
                border.col='white',
                palette=c('gray10', 'gray40', 'gray70'))

```
# 
It is likely that the short-term rental market follows a similar market hierarchy, however, we can imagine that a few different spatial features can influence the short-term market.  While there are many possible additional features, we consider two to be the most likely to influence rates or occupancy: 1) Proximity to beach; and 2) Proximity to key tourist activities and events.  Using the three broad submarkets from the long-term market (inner, middle and outer) we have created a five sub-market system as a starting point for spatially analysing short and long term ltrals in Melboure:

```{r core_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

```{r beachbuffer, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  suppressWarnings(beach_buffer <- st_buffer(beach_sf, dist =(500 / m_conv)))

```{r add_st_space, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  # Convert to point sf data
   str_sf <- st_as_sf(str_tdf %>% 
                        dplyr::select(property_id, longitude, latitude),
                      coords = c('longitude', 'latitude'),
                      crs = 4283)

   ltr_sf <- st_as_sf(ltr_tdf %>% 
                        dplyr::select(addr_id, longitude, latitude) %>%
                        dplyr::filter(!is.na(latitude)),
                      coords = c('longitude', 'latitude'),
                      crs = 4283)

  # Add suburb designation and remove those that are outside

   str_sf <- st_join(str_sf, 
                     sub_sf %>% 
                      dplyr::select(suburb = NAME_2006,
                                    sub_des = suburbDesi,
                                    geometry)) %>%
   dplyr::filter(!is.na(sub_des))

   ltr_sf <- st_join(ltr_sf, 
                     sub_sf %>% 
                       dplyr::select(suburb = NAME_2006,
                                     sub_des = suburbDesi,
                                     geometry)) %>%
   dplyr::filter(!is.na(sub_des))

Determine which suburbs are represented in both datasets and trim to those observations

```{r match_suburbs, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

    sub_str <- str_sf %>% 
      dplyr::select(suburb, -geometry) %>% 
      as.tibble() %>%
      dplyr::group_by(suburb) %>% 
      dplyr::summarize(count=n())

    sub_ltr <- ltr_sf %>% 
      dplyr::select(suburb, -geometry) %>% 
      as.tibble() %>%
      dplyr::group_by(suburb) %>% 
      dplyr::summarize(count=n())

    str_sf <- str_sf %>%
      dplyr::filter(suburb %in% sub_all$suburb)

    ltr_sf <- ltr_sf %>%
      dplyr::filter(suburb %in% sub_all$suburb)

Next we add the sa1 and beach designations

```{r add_sa1_beach, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  # Add SA1
    str_sf <- st_join(str_sf, 
                       sa1_sf %>%
                         dplyr::select(sa1=SA1_MAIN11,
                                       geometry)) %>%
    dplyr::filter(!is.na(sa1))

    ltr_sf <- st_join(ltr_sf, 
                       sa1_sf %>%
                         dplyr::select(sa1=SA1_MAIN11,
                                       geometry)) %>%
    dplyr::filter(!is.na(sa1))

  # Add Beach
   str_sf <- st_join(str_sf, 
                       beach_buffer %>%
                         dplyr::select(beach=id,
                                       geometry)) %>%
             dplyr::mutate(beach = ifelse(is.na(beach), 0, beach))

   ltr_sf <- st_join(ltr_sf, 
                       beach_buffer %>%
                         dplyr::select(beach=id,
                                       geometry)) %>%
             dplyr::mutate(beach = ifelse(is.na(beach), 0, beach))

Add market designations.

```{r convert_st_subm, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  ## Add to STR

   # Add individual classes
   str_sf$geo_mrkt <- 'rural'
   str_sf$geo_mrkt[str_tdf$sub_des == 'Middle'] <- 'suburban'
   str_sf$geo_mrkt[str_tdf$sub_des == 'Inner'] <- 'city'
   str_sf$geo_mrkt[str_tdf$suburb %in% core_suburbs] <- 'city-core'
   str_sf$geo_mrkt[str_tdf$beach == 1] <- 'beach'

   # Order the factors properly
   str_sf$geo_mrkt <- factor(str_sf$geo_mrkt,
                               levels=c('city-core', 'city', 'suburban',
                                        'rural', 'beach'))

   ## Add to LTR

   # Add individual classes
   ltr_sf$geo_mrkt <- 'rural'
   ltr_sf$geo_mrkt[ltr_sf$sub_des == 'Middle'] <- 'suburban'
   ltr_sf$geo_mrkt[ltr_sf$sub_des == 'Inner'] <- 'city'
   ltr_sf$geo_mrkt[ltr_sf$suburb %in% core_suburbs] <- 'city-core'
   ltr_sf$geo_mrkt[ltr_sf$beach == 1] <- 'beach'

   # Order the factors properly
   ltr_sf$geo_mrkt <- factor(ltr_sf$geo_mrkt,
                               levels=c('city-core', 'city', 'suburban',
                                        'rural', 'beach'))
   # Count Cleaning
   countCleaning('location')

@@

```{r ltprice_fltr, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@

```{r exch_rate_adj, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@

```{r ltprice_fltr3, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

@@
